### 2018-01-22 Paper/jaccardbaetica.tex
material and method 1st part

We analysed a dataset of 131 stamps from 81 workshops. All the dataset was collected from CEIPAC database (citar). The workshops were located in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance. The chronology detected in the workshop is widely diverse from I-III B.C. However, all the workshops presented a long activity of production being difficult to specify a accurate chronology.

%hablar de la cronologia

%los sellos fueron marcados a partir del siglo II d.C (la economía oleícola bética Remesal)

@@

This method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. Unlike Jaccard distance, Morisita-Horn variant can be used to handle large samples with different sizes and diversity. The index can be described  where 0 is no presence of overlap and 1 totally similarity. 
%hablar sobre Horn (Morisita)

>>>>

We analysed a dataset of 990 stamps from 81 workshops. From the dataset, a sample of 131 different stamps were identified and collected from from CEIPAC database (citar). The workshops were located in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance. The chronology in the workshops is widely diverse from I-III B.C. However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason can be that most of them were partially excavated focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

%los sellos fueron marcados a partir del siglo II d.C (la economía oleícola bética Remesal) hablar de stams más concreto

@@

This method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. Unlike Jaccard distance, Morisita-Horn variant can be used to handle large samples with different sizes and diversity. In our case, our dataset shows a sample not uniform so this method is useful when sets show a diversity amongst samples.

%escribir un poco más 
The index can be described  where 0 is no presence of overlap and 1 totally similarity. 
%hablar sobre Horn (Morisita)hablar sobre que el sample no estaba uniforme por eso usamos el morisita horn

\section{Results}

\section{Discussion and Conclusion}
